\huge{Comment on `The Limits of Cosmic Shear'}

### 2016-12-02 Limber_Comment.tex
Re-arranging sections so theory comes first

\author{Members of the KiDS, DES, HSC, CFHTLenS and RCSLenS collaborations\altaffilmark{1} ....}
%\email{tbd@tbd}

\altaffiltext{1}{Aim is for representatives from each survey to sign}

\begin{abstract}
Kitching et al. (2016) examine the impact of four approximations that can be used when constraining cosmological parameters from the measurement of weak gravitational lensing by large-scale structures, also known as cosmic shear.  We support the core important message of this paper that the use of such approximations should be carefully considered in the future analysis of high precision surveys such as Euclid, LSST and WFIRST.  In this comment, we argue that these approximations are not able to explain away the tension between the constraints from some current weak lensing surveys and Planck.  Reducing uncertainty and characterising bias in photometric redshift estimation is certainly a crucial task for the success of current and future surveys.  We highlight that sophisticated treatments of these uncertainties have already been explored in the literature and have been shown not to resolve the tension with Planck, in contrast to the message that Kitching et al. (2016) convey.

@@

In this comment paper we discuss four approximations that can be used when deriving theoretical predictions for the principally used cosmic shear statistic, $\xi_\pm$, the two-point shear correlation function.   These approximations have been explored in (ADD REF) and most recently highlighted by \citet{kitching/etal:2016} as a way to reduce tensions between weak lensing and CMB experiments, focusing on a re-analysis of the non-tomographic weak lensing data from the CFHTLenS survey \citep{kilbinger/etal:2013}.    In section~\ref{sec:cfhtlens} we compare the `one-parameter' cosmological re-analysis of \citet{kitching/etal:2016} with the full six-parameter analysis by \citet{kilbinger/etal:2013}, arguing that this particular non-tomographic data set is not in significant tension with Planck.  We also briefly review the literature that has advanced our understanding since the original CFHTLenS analyses were published.  In section~\ref{sec:theory} we clarify that only one/two? of the approximations highlighted by \citet{kitching/etal:2016} have actually been used in recent weak lensing analyses \citep{joudaki/etal:2016, hildebrandt/etal:2016, joudaki/etal:2017} and discuss why we do not expect these approximations to impact on the cosmological analysis of these surveys.    Finally in section~\ref{sec:photoz} we review our current knowledge of photometric redshift uncertainties and the sophisticated mitigation strategies that have already been applied to data.  We suggest that a possible misinterpretation in the direction of the redshift biases reported in \citet{choi/etal:2016} has lead to the incorrect conclusion of \citet{kitching/etal:2016} that these redshift biases can resolve the tension with Planck.

%-the analysis in the Kitching et al paper is fine, but the approximations used are not able to explain away the tension with Planck results, in contrast to the message the paper conveys.
%- we have verified that current (KiDS450) analyses are barely affected because they are restricted to larger scales
%- the CFHTLenS analysis used as an example has larger errors than the marginal error quoted in Kitching et al, and deviates less from Planck than most other results
%- the Limber and flat-sky approximations barely move this data point, so do not resolve even this tension
%- the discussion on photo-z uncertainties, where the uncertainty is characterized by a simple shift in the mean, is oversimplified and does not apply to more sophisticated treatment as used in latest results

>>>>

\author{Members of the KiDS, CFHTLenS and RCSLenS collaborations\altaffilmark{1} ....}
%\email{tbd@tbd}

%\altaffiltext{1}{}

\begin{abstract}
Kitching et al. (2016) examine the impact of the flat-sky and Limber approximations that can be used when constraining cosmological parameters from the measurement of weak gravitational lensing by large-scale structures, also known as cosmic shear.  We support the core message of this paper that the use of such approximations should be considered in the future analysis of high precision surveys such as Euclid, LSST and WFIRST.  In this comment, we argue that these approximations have negligible impact for current surveys and are not able to explain away the tension between the constraints from some current weak lensing surveys and Planck.  Reducing uncertainty and characterising bias in photometric redshift estimation a critical task for the success of current and future surveys.  We highlight that sophisticated treatments of these uncertainties have already been explored in the literature and have been shown not to resolve the tension with Planck, in contrast to the message that Kitching et al. (2016) convey.

@@

In this comment paper we discuss the flat sky and Limber approximations that can be used when deriving theoretical predictions for the principally used cosmic shear statistic, $\xi_\pm$, the two-point shear correlation function.   The Limber approximation for cosmic shear has been previously explored by \citet{giannantonio/etal:2012} finding that it provided sufficient accuracy for future cosmic shear studies.  Recently \citet{kitching/etal:2016} highlighted that considering the flat sky and Limber approximations in concert can reduce tensions between weak lensing and CMB experiments, focusing on a re-analysis of the non-tomographic weak lensing data from the CFHTLenS survey \citep{kilbinger/etal:2013}.

In section~\ref{sec:theory} we clarify that which brand of approximations highlighted by \citet{kitching/etal:2016} have been used in recent weak lensing analyses \citep{joudaki/etal:2016, hildebrandt/etal:2016, joudaki/etal:2017} and show that we are unable to re-produce their conclusions.  We therefore do not expect these approximations to impact on the cosmological analysis of current surveys.    In section~\ref{sec:cfhtlens} we compare the `one-parameter' cosmological re-analysis of \citet{kitching/etal:2016} with the full six-parameter analysis by \citet{kilbinger/etal:2013}, arguing that this particular non-tomographic data set was never in significant tension with Planck.  We also briefly review the literature that has advanced our understanding since the original CFHTLenS analyses were published.

Finally in section~\ref{sec:photoz} we review our current knowledge of photometric redshift uncertainties and the sophisticated mitigation strategies that have already been applied to data.  We suggest that a possible misinterpretation in the direction of the redshift biases reported in \citet{choi/etal:2016} has lead to the incorrect conclusion of \citet{kitching/etal:2016} that these redshift biases can resolve the tension with Planck.

### 2016-12-02 theory.tex
Re-arranging sections so theory comes first

\begin{table}
\label{tab:Tl_nu}
\begin{center}
\begin{tabular}{ | l | c | c  | c |}
\hline
Case & $T_\ell$ & $\nu$ & Used in \\ \hline
\citet{kitching/etal:2016} `Standard' & $1$ & $\ell$ & pre-2014 CFHTLenS papers \\
Baseline Limber Flat Sky &  $\ell^4 / (\ell + 0.5)^4$ & $\ell$ & \\
Baseline Limber Spherical & equation~\ref{eqn:Tl} & $\ell$ & \\
Extended Limber Flat Sky & $\ell^4 / (\ell + 0.5)^4$ & $\ell + 0.5$ & \\
Extended Limber Spherical & equation~\ref{eqn:Tl}& $\ell + 0.5$  & \\
Extended `Standard' & $1$ & $\ell + 0.5$ & \citet{joudaki/etal:2016} \&  \\
  & & & \citet{hildebrandt/etal:2016}  \\\hline
 \end{tabular}
 \end{center}
 \caption{Variations on the different approximations that can be made when calculating the convergence power spectrum $P_\kappa(\ell)$ (equation~\ref{eqn:Pkappa}), using a Limber approximation.}
 \end{table}

>>>>

 \begin{table}[htb]
\label{tab:Tl_nu}
\begin{center}
\begin{tabular}{ | l | c | c  | c |}
\hline
Case & $T_\ell$ & $\nu$ & Used in \\ \hline
\citet{kitching/etal:2016} `Standard' & $1$ & $\ell$ & pre-2014 CFHTLenS papers \\
Baseline Limber Flat Sky &  $\ell^4 / (\ell + 0.5)^4$ & $\ell$ & \\
Baseline Limber Spherical & equation~\ref{eqn:Tl} & $\ell$ & \\
Extended Limber Flat Sky & $\ell^4 / (\ell + 0.5)^4$ & $\ell + 0.5$ & \\
Extended Limber Spherical & equation~\ref{eqn:Tl}& $\ell + 0.5$  & \\
Extended `Standard' & $1$ & $\ell + 0.5$ & \citet{joudaki/etal:2016} \&  \\
  & & & \citet{hildebrandt/etal:2016}$^*$\\\hline
 \end{tabular}
 \end{center}
 \caption{Variations on the different approximations that can be made when calculating the convergence power spectrum $P_\kappa(\ell)$ (equation~\ref{eqn:Pkappa}), using a Limber approximation.  $^*$We confirm that there is a typographical error in equation 4 of \citet{hildebrandt/etal:2016} which does not include the extra factor of 0.5 in $\nu$ that was incorporated in the cosmological analysis.}  
 \end{table}
